Turbulence in compact to giant HII regions

### 2022-01-25 Corr.tex
Javier changes 2022-01-22

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &             log $R$ &   0.69 $\pm$ 0.07 &   -0.83 $\pm$ 0.12 &   0.98 &    < 10\(^{-4}\) \\
 log $\sigma$ &            log L(H) &   0.25 $\pm$ 0.10 &  -8.90 $\pm$ 3.63 &   0.83 &  0.003 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.78 $\pm$ 0.46 &  -0.17 $\pm$ 0.54 &   0.66 &  0.036 \\
      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &    1.21 $\pm$ 0.16 &  -0.59 &  0.072 \\
 log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.19 &   0.65 $\pm$ 0.12 &   0.54 &  0.103 \\
      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &    0.11 $\pm$ 0.18 &   -0.42 &  0.227 \\
      log $m$ &         log $r_{0}$ &   -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.38 &   0.27 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
    log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
 log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

### 2022-01-25 strucfunc_paper.tex
Javier changes 2022-01-22

\subsection{Physical properties of the sample regions}
\label{sec:regions-milky-way}

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 2.7    \\
30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

%Size vs correlation length
\textit{Note: Regarding the values and uncertainties of the size of the regions, table \ref{tab:regions-properties},  I was fearing that they might seem kind of arbitrary for the reviewers. So I had the idea of using the box size value instead of the size, and the box size minus the maximun separation r for the uncertainty for the regression analysis (not shown). The results are quite consistent with the size, R, value (see lines below) giving $\log r_0 = (0.77 \pm 0.12) \log box size-(0.80 \pm 0.18)$. There is a diminution for the Pearson correlation value from 0.98 to 0.95 and the p-value changes from 3.7e-07 to 4.49e-05.}
The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region. The relationship we found is relation of \(\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)\).

The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.25 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(9 \pm 4.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 1.4) \log \sigma -(36 \pm 1)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/rvsR}
\caption{The log $r_0$-log $R$ plane derived form our results an data in the literature. A fit with slope of 0.67$\pm$0.07 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis. }
\label{fig:rvsR}
\end{figure}

>>>>

\subsection{Physical properties of the sample regions. }
\label{sec:regions-milky-way}

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   22.4 \pm 2.7    \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

%Size vs correlation length
The Figure \ref{fig:rvsR} shows the relation of the correlation length $r_0$ and the size \(S\) of the region. The relationship we found is relation of \(\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)\).

The Figure \ref{fig:sigvsl} shows the log \(\sigma\)-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.25 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(9 \pm 4.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 1.4) \log \sigma -(36 \pm 1)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/rvsS}
\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature. A fit with slope of 0.67 $\pm$ 0.07 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis. }
\label{fig:rvsR}
\end{figure}
